Joint analysis of read count data

### 2020-09-09 combined_analysis/combine_all_data.Rmd
add zenith

METADATA$Reported_Gender = factor(METADATA$Reported_Gender)
METADATA$Dx = factor(METADATA$Dx, c("BP", "Control", "SCZ"))

form = ~ 0 + Dx*Reported_Gender + RIN + ageOfDeath + scale(IntronicRate)*Cohort + scale(IntragenicRate)*Cohort + scale(IntergenicRate)*Cohort + scale(rRNARate)*Cohort + (1|Institution:Cohort) + (1|Region:Cohort) + (1|Individual_ID)

@@

# SCZ by sex
L_SCZ = Lbase
L_SCZ['DxSCZ:Reported_GenderMale'] = 1
L_SCZ['DxControl:Reported_GenderMale"'] = -1
L_SCZ['DxSCZ'] = -1
L_SCZ['DxControl'] = 1 
# (A - B) - (C - D) = A - B - C + D

@@

L = cbind(	SczSex = L_SCZ)#,
			# BPSex = L_BP)

>>>>

# METADATA$Reported_Gender = factor(METADATA$Reported_Gender)
# METADATA$Dx = factor(METADATA$Dx, c("BP", "Control", "SCZ"))

form = ~ Dx*Reported_Gender + RIN + ageOfDeath + scale(IntronicRate)*Cohort + scale(IntragenicRate)*Cohort + scale(IntergenicRate)*Cohort + scale(rRNARate)*Cohort + (1|Institution:Cohort) + (1|Region:Cohort) + (1|Individual_ID)

@@

# SCZ by sex
# L_SCZ = Lbase
# L_SCZ['DxSCZ:Reported_GenderMale'] = 1
# L_SCZ['DxControl:Reported_GenderMale'] = -1
# L_SCZ['DxSCZ'] = -1
# L_SCZ['DxControl'] = 1 
# (A - B) - (C - D) = A - B - C + D

@@

L_SCZ = Lbase
L_SCZ['DxSCZ:Reported_GenderMale'] = 1

L_BP = Lbase
L_BP['DxBP:Reported_GenderMale'] = 1

L = cbind(	SczSex = L_SCZ,
			BPSex = L_BP)
